---
title: "Monoidal Estimators"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Monoidal Estimators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(monoidalEstimator)
```

# Cumulative Risk

The `causalRisk` package provides an estimator of the cumultative distribution of right-censored outcomes:

\[
\widehat{\Pr}(Y < t) = \frac{1}{n} \sum_{i = 1}^n \frac{\Delta_i I(Y_i < t)} { {\widehat{\Pr}} (\Delta_i = 1)}
\]

where $\Delta = I(Y < C)$ with a bit of algebra we can write this function as:

\[
\widehat{\Pr}(Y < t) =  h \circ g(f_1f_2)
\]

where:


\[
f_1(t) = I(Y_i < t)/1
\]

\[
f_2(t) = \frac{\Delta_i}{ {\widehat{\Pr}} (\Delta_i = 1) }
\]

\[
g(t) = f_1(t) \cdot f_2(t))
\]

\[
h(t) = \frac{ \sum_i g(t)}{ \sum_i 1 }
\]
  
Elements of the estimator:

```{r}
f1 <- function(vs){
  Ti <- vs$V1
  function(t){
    (Ti < t) * 1
  }
}

f2 <- function(vs){
  del <- vs$V2
  function(t){
    (del < t) * 1
  }
}
```

Composing the estimator: 

```{r}
fs <- list(f1, f2)
cumrisk <- make_estimator(fs)
```

The data:
```{r}
dt <- data.frame(
  V1 = rexp(10),
  V2 = rexp(10)
)
dt <- purrr::transpose(as.list(dt))
```

Bind data to the estimator:

```{r}
crisk <- cumrisk(dt)
crisk(c(0.2, 0.3, 0.5, 0.8, 1, 6, 10))

```


